---
title: "#Spreadsheet programs for scientific data"
author: "C. A. Hamm"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Code of Conduct
Data Carpentry is dedicated to providing a harassment-free experience for everyone, regardless of gender, sexual orientation, disability, physical appearance, body size, race, nationality, religion, or choice of text editor. We do not tolerate harassment of participants in any form.

## Code of Conduct
Harassment includes offensive verbal comments related to gender, sexual orientation, disability, physical appearance, body size, race, religion, sexual images in public spaces, deliberate intimidation, stalking, following, harassing photography or recording, sustained disruption of talks or other events, inappropriate physical contact, and unwelcome sexual attention.

## Code of Conduct
+ All communication should be appropriate for a professional audience including people of many different backgrounds. Sexual language and imagery is not appropriate for any event or communication.
+ Be kind to others. Do not insult or put down other participants.
+ Behave professionally. Remember that harassment and sexist, racist, or exclusionary jokes are not appropriate.
+ Participants asked to stop any harassing behavior are expected to comply immediately. Participants violating these rules may be asked to leave the event or cease corresponding with the community at the sole discretion of the organizers without a refund of any charge that may have been levied.

## Code of Conduct
Thank you for helping make this a welcoming, friendly community for all.

[Code of Conduct](http://www.datacarpentry.org/code-of-conduct/)

Please speak with an instructor or email Tracy Teal if you have any concerns: tkteal@datacarpentry.org

## Requirements

Data Carpentry 


## The importance of data

Good **data organization** is critical for a successful research project. Spreadsheets can play an important role in research because they allow for easy data entry.


## Lesson outline
In this lesson we will cover:

- Good data entry practices
- Avoid common formatting mistakes
- Quality control and manipulation
- Exporting data from spreadsheets

In short, **best practices** for handling data.

## Data

The data we will use for this lesson are availaible here:

[Lesson data](https://ndownloader.figshare.com/files/2252083) 

https://ndownloader.figshare.com/files/2252083

## Slide with Plot

```{r pressure}
plot(pressure)
```

